Quality Assessment of OpenStreetMap Footpath Data

### 2020-08-19 report/report.tex
Add constraint about building taper
Add notes to urban planning feasibility discussion

\begin{enumerate}
    \item The program will not handle terrain features and altitude. It will be assumed that the road mesh can be projected on a flat 2d surface without feature intersection.
    \item It will be assumed that the city map consists of only arterial (primary) roads, secondary roads, residential roads and footpaths.
    \item It will be assumed that the OSM dataset represents all roads as simple polylines, and building footprints as simple connected polygons. Any other features (such as squares, which are roads represented as polygons) will be omitted from the dataset.
    \item The road network is assumed to be a 2D simple graph. This means that any overlapping roads, such as tunnels and bridges that cross over street-level roads, will be eliminated from the dataset. Any self-connected nodes will also be eliminated from the dataset.
\end{enumerate}

@@

For simple presentation in e.g. animation and video games or even urban planning software, such procedurally generated cities could very well be enough.
As said however, the big problem is that these features will rarely match real life.
Such models will be sufficient as long as one can be satisfied with looking at rough representations of buildings and does not require additional knowledge about minor features.
However, many studies in urban development have been done before that required detailed knowledge about a city's geometry, e.g. for the purposes of modeling heat development
\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)}
or reducing noise
\textbf{(Joon, Seo and Byung, 2011)}.

By looking at such studies in urban development, one will discover that a lot of research in this field requires detailed morphological information that goes beyond simply knowing the geometry of the city.
Urban architects often work with morphological structures where a single feature, such as a city neighborhood, can be examined from many different levels of perspective.
A neighborhood can be analyzed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Similarly a road network can be analyzed by looking at it either at its connectivity by viewing it a a simple 2D graph, but it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morphological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
According to \textbf{(Stojanovski, 2019)}, this type of representation is known as a multimodal structures, due to the possibility of incorporating multiple modes of transportation, but it may even describe subtilties like building facades and distances between curb line and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
For media applications, such morphological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of way finding to create logical routes for different types of traffic.
But for urban planners requiring an exact morphological representation of some specification, this complementary data will have to be obtained from another dataset.

>>>>

\begin{enumerate}
    \item The program will not handle terrain features and altitude. It will be assumed that the road mesh can be projected on a flat 2d surface without feature intersection.
    \item It will be assumed that the city map consists of only arterial (primary) roads, secondary roads, residential roads and footpaths.
    \item It will be assumed that the OSM dataset represents all roads as simple polylines, and building footprints as simple connected polygons. Any other features (such as squares, which are roads represented as polygons) will be omitted from the dataset.
    \item The road network is assumed to be a 2D simple graph. This means that any overlapping roads, such as tunnels and bridges that cross over street-level roads, will be eliminated from the dataset. Any self-connected nodes will also be eliminated from the dataset.
    \item All building footprints are assumed to be coherent to their footprints along the z axis. Thus, it will be assumed that no buildings taper or extend beyond their footprints at a higher altitude.
\end{enumerate}

@@

Simple, procedurally generated cities, populated with generic 3D models, could very well be enough for simple presentation in e.g. animation and video games or even urban planning software, 
In such a model however, features will only be rough representations, and rarely match their real life counterparts.
Such models will be sufficient as long as one can be satisfied with looking at rough representations of major features, and do not require additional knowledge about minor features.
It turns out however, that many studies in urban development have a highly case-by-case nature.
Studies acroos many different areas have been done before that required very different knowledge about a city's geometry, e.g. for the purposes of modeling heat development
\textbf{(Nakata-Osaki, Souza and Rodrigues, 2018)}
or reducing noise
\textbf{(Joon, Seo and Byung, 2011)}.

According to \textbf{(Stojanovski, 2019)}, software that strives to aid in the urban development process is commonly not sophisticated enough to fully represent the needs and workspaces of urban planners in practise.
Stojanovski goes on to claim that a lot of research in this field requires detailed information that goes beyond simply knowing the geometry of the city.
Additionally, such research also typically requires additional logical data structures that a OSM cannot note serve.
Urban architects often work with morphological structures where a single feature, such as a city neighborhood, can be examined from many different levels of perspective.
A neighborhood can be analyzed from the level of its city blocks, individual lots, properties or building limits, building facades or even indoor spaces.
Similarly a road network can be analyzed by looking at it either at its connectivity by viewing it a a simple 2D graph, but it might as well be seen as a hierarchical structure where primary roads branch off into sub-streets. 
The very unfortunate fact is that much of that morphological information is not present in the OSM dataset.
Furthermore, take the fact that even a single road can be comprised of many different sections with different purposes.
A single inner-city street for example, often contains sidewalks and lanes reserved for taxis or public transit, all of a certain placement and dimension that determines what type of traffic it can serve.
This type of representation is known as a multimodal structures, due to the possibility of incorporating multiple modes of transportation, but it may even describe subtilties like building facades and distances between curb line and building lot.
OSM, while being an excellent source of city geometry, is simply not a sophisticated enough dataset to cater to all these possible areas of research.
For media applications, such morphological and multimodal information could in theory be generated procedurally, by using shape grammars and some sort of way finding to create logical routes for different types of traffic.
For urban planners however, requiring an exact representation of some specification, this complementary data will have to be obtained from another dataset.
It may also be necessary for a researcher to implement their own data structures on top of the existing city model, with will increase the complexity of the problem even further.
The case-by-case nature of urban development projects also means that it is unlikely that a single piece of software can cater to the very differing needs of data and data structures for variuos projects.
